Data Specialization for a Staged Lambda Calculus

### 2015-02-28 paper/appendix.tex
put in the output of trie

\begin{lstlisting} 
datatype _ = EmptyS | ConsS of _
datatype _ = EmptyL | ConsL of _
fun partition l =
 case l of
   EmptyL => (false,EmptyL,EmptyL,EmptyL)
 | ConsL (s,ss) =>
     let (anyEmpty,a,b,c) = partition ss in
     case unroll s of
       EmptyS => (true,a,b,c)
     | ConsS (z,zs) =>
         case z of 
           A => (anyEmpty, ConsL(zs,a), b, c) 
         | B => (anyEmpty, a, ConsL(zs,b), c) 
         | C => (anyEmpty, a, b, ConsL(zs, c))
fun exists1 (l,s) = roll ((), 
 case l of 
   EmptyL => inj1 ()
 | ConsL _ => 
   let (anyEmpty, a, b, c) = partition l in
   inj2 (
   	if anyEmpty then inj1 () else inj2 (), 
   	#2 (exists1 (a,())), 
   	#2 (exists1 (b,())), 
   	#2 (exists1 (c,()))
   )
 )

datatype _ = EmptyS | ConsS of _
fun exists2 ((l,s), p) =
 case unroll p of 
   inj1 () => false
 | inj2 (anyEmpty,p_a,p_b,p_c) => 
     case s of
       EmptyS => 
         case anyEmpty of 
           inj1 () => true 
         | inj2 () => false
     | ConsS (z,zs) =>
         case z of
           A => exists2 (((),zs),p_a)
         | B => exists2 (((),zs),p_b)
         | C => exists2 (((),zs),p_c)
\end{lstlisting}

>>>>

\begin{lstlisting}

datatype trie = Leaf 
			  | Branch of bool * trie * trie * trie

1`datatype letter = A | B | C 
datatype string = EmptyS | ConsS of letter * string
datatype list   = EmptyL | ConsL of string * list
fun partition (EmptyL) = (false,EmptyL,EmptyL,EmptyL) 
  | partition (ConsL (s,ss)) = 
  let val (anyEmpty,a,b,c) = partition ss in 
  case s of 
    EmptyS => (true,a,b,c) 
  | ConsS (A,z) => (anyEmpty,ConsL(z,a),b,c) 
  | ConsS (B,z) => (anyEmpty,a,ConsL(z,b),c) 
  | ConsS (C,z) => (anyEmpty,a,b,ConsL(z,c)) 
in
fun exists (EmptyL,()) = ((), Leaf)
  | exists (ConsL ht,()) =
	let 
	  val (anyEmpty,a,b,c) = partition (ConsL ht) 
	in ((), 
		Branch (anyEmpty, 
			#2 (exists (a, ())), 
			#2 (exists (b, ())), 
			#2 (exists (c, ()))))

`2`datatype letter2 = A2 | B2 | C2
datatype string2 = EmptyS2 | ConsS2 of letter2 * string2
fun exists (((),s), Leaf) = false
  | exists (((),s), Branch (e,a,b,c)) = 
    case s of
	  EmptyS2 => e
	| ConsS2 (A,z) => exists (((), z), a)
	| ConsS2 (B,z) => exists (((), z), b)
	| ConsS2 (C,z) => exists (((), z), c)`

\end{lstlisting}
